Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-05-07 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Shortened a few equation variables and fixed a few confusing sentences.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4610 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\setlength{\arraycolsep}{0.0em}
\begin{multline}
\label{eq:lookahead_cost}
Cost_{Total}(r) = \sum_{\forall l \in RT(i,r)} Cost(l) + \alpha \times ExpectedCost(r,j)
\end{multline}
\setlength{\arraycolsep}{5pt}

where \textit{RT(i,r)} is the set of all routing nodes used so far from \textit{i} to \textit{r} and $\alpha$ is a constant number that determines the aggressiveness of the directed search. $\alpha$ is 1.2 by default in VPR. VPR's original $ExpectedCost(n,j)$ function is~\cite{betz1999architecture}:

\setlength{\arraycolsep}{0.0em}
\begin{multline}
\label{eq:expected_routing_cost}
ExpectedCost(r,j) = Criticality_{fac} \times T_{delay} + \\(1 - Criticality_{fac}) \times ExpectedCongestionCost(r,j)
\end{multline}
\setlength{\arraycolsep}{5pt}

@@

\begin{multline}
\label{eq:tdelay}
T^\prime_{delay} = T_{delay} + T_{interposer} \times ExpectedInterposerHops
\end{multline}
\setlength{\arraycolsep}{5pt}

We modify $ExpectedCongestionCost(r,j)$ in (\ref{eq:expected_routing_cost}) in a similar way to account for the new interposer routing nodes.

@@

Moreover, better performance can be achieved if either of these two options is used together with bidirectional interposer wires. Enabling \textit{fanout transfer} with bidirectional interposer wires (column \textit{d} in Figure~\ref{fig:all_arch_experiments}) reduces the minimum channel width by 9\% and critical path delay by 0.7\%. Enabling \textit{fanin transfer} with bidirectional interposer wires (column \textit{e} in Figure~\ref{fig:all_arch_experiments}) has an even stronger impact and reduces the minimum channel width by 10\% and critical path delay by 0.7\%. This signifies that added flexibility to drive an interposer wire is more important for routability compared to adding flexibility of having an interposer wire drive multiple vertical routing wires on the other side of the cut.

>>>>

\setlength{\arraycolsep}{0.0em}
\begin{multline}
\label{eq:lookahead_cost}
Cost_{Total}(r) = \sum_{\forall l \in RT(i,r)} Cost(l) + \alpha \times ExpectCost(r,j)
\end{multline}
\setlength{\arraycolsep}{5pt}

where \textit{RT(i,r)} is the set of all routing nodes used so far from \textit{i} to \textit{r} and $\alpha$ is a constant number that determines the aggressiveness of the directed search. $\alpha$ is 1.2 by default in VPR. VPR's original $ExpectCost(n,j)$ function is~\cite{betz1999architecture}:

\setlength{\arraycolsep}{0.0em}
\begin{multline}
\label{eq:expected_routing_cost}
ExpectCost(r,j) = Criticality_{fac} \times T_{delay} + \\(1 - Criticality_{fac}) \times ExpectCongestionCost(r,j)
\end{multline}
\setlength{\arraycolsep}{5pt}

@@

\begin{multline}
\label{eq:tdelay}
T^\prime_{delay} = T_{delay} + T_{interposer} \times ExpectInterposerHops
\end{multline}
\setlength{\arraycolsep}{5pt}

We modify $ExpectCongestionCost(r,j)$ in (\ref{eq:expected_routing_cost}) in a similar way to account for the new interposer routing nodes.

@@

Moreover, better performance can be achieved if either of these two options is used together with bidirectional interposer wires. Enabling \textit{fanout transfer} with bidirectional interposer wires (column \textit{d} in Figure~\ref{fig:all_arch_experiments}) reduces the minimum channel width by 9\% and critical path delay by 0.7\%. Enabling \textit{fanin transfer} with bidirectional interposer wires (column \textit{e} in Figure~\ref{fig:all_arch_experiments}) has an even stronger impact and reduces the minimum channel width by 10\% and critical path delay by 0.7\%. This signifies that added flexibility to drive an interposer wire is more important for routability than added flexibility allowing an interposer wire to drive multiple vertical routing wires on the other side of the cut.
